---
title: "Playing with Webscraping"
author: "KevinHo"
date: "15 February 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## About

This is my first exercise in webscraping using rvest
I'm following the tutorial listed [here](https://blog.rstudio.org/2014/11/24/rvest-easy-web-scraping-with-r/).
And the CRAN repository is [here](https://cran.r-project.org/web/packages/rvest/index.html)

## Setup

I'll be using the rvest package and I'll be scraping data from imdb.

*NB: The `html()` function is no deprecated and replaced with the `read_html()` function.*

```{r setupB}
library(rvest)

lego_movie <- read_html("http://www.imdb.com/title/tt1490017/")
```

## Get the data
Use [selectorgadget](http://selectorgadget.com/) to find out which css selector we want to grab the data.

Then we'll use `html_node()` to find the first node that matches the selector, extract the contents with `html_text()` and then convert it to a number using `as.numeric()`

```{r getData}
lego_movie %>%
    html_node("strong span") %>%
    html_text() %>%
    as.numeric()
```


## My own version

Now that I've run through the tutorial. Here is my own application

```{r asxscrape}
pANZ <- read_html("https://www.google.com/finance?cid=675233")

pANZ %>%
    html_node("#price-panel .pr") %>%
    html_text() %>%
    as.numeric()

```
